---
title: "PubMed Weekly Report"
author: "Sophia Cofone"
output:
  pdf_document: default
  html_document: default
---

```{r setup, echo=FALSE}
library(knitr)
```

```{r, echo=FALSE, message=FALSE}
# 1. Library
require(RMySQL)
library(sqldf)

# 2. Settings
# db_user <- 'root'
# db_password <- 'password'
# db_host <- 'localhost'
# db_port <- 3306

### starSchemaAuthor ###
# 3. Initial connection
dbcon_mysqlA <-  dbConnect(MySQL(), user = db_user, password = db_password,
                   host = db_host, port = db_port, local_infile=TRUE)

invisible({dbSendQuery(dbcon_mysqlA, "set global local_infile=true;")})

# 5. Update Settings/connection
db_name <- 'starSchemaAuthor'

# update connection
dbcon_mysqlA <-  dbConnect(MySQL(), user = db_user, password = db_password,
                 dbname = db_name, host = db_host, port = db_port, local_infile=TRUE)

# 3. Initial connection
dbcon_mysqlJ <-  dbConnect(MySQL(), user = db_user, password = db_password,
                   host = db_host, port = db_port, local_infile=TRUE)

invisible({dbSendQuery(dbcon_mysqlJ, "set global local_infile=true;")})

# 5. Update Settings/connection
db_name <- 'starSchemaJournal'

# update connection
dbcon_mysqlJ <-  dbConnect(MySQL(), user = db_user, password = db_password,
                 dbname = db_name, host = db_host, port = db_port, local_infile=TRUE)
```

# This report is to provide an update on the top authors and publications in the PubMed data.

## Summary table of top ten authors with the most publications
```{r, echo=FALSE, message=FALSE}
mysql_query <- "SELECT last_name, fore_name, articles_author, initials FROM AuthorFact 
ORDER BY articles_author DESC 
LIMIT 10"

top_10_a = dbGetQuery(dbcon_mysqlA, mysql_query)

top_10_a_noi <- subset(top_10_a, select = -ncol(top_10_a))

kable(top_10_a_noi, align = c("l", "l","l"), col.names = c("Last Name", "Fore Name", "Number of Articles"))
```
```{r, echo=FALSE, message=FALSE}

library(ggplot2)

# create chart
  authorplot <- ggplot(top_10_a, aes(x=reorder(initials, -articles_author), y=articles_author, fill=articles_author)) +
  geom_col() +
  scale_fill_gradient(low="blue", high="red") + 
  ggtitle("Number of Publications by Author") +
  xlab("Author") +
  ylab("Top Authors by Publications") +
  theme_light() +
  geom_text(aes(label=articles_author), vjust=2, color="white", size=4)

authorplot

```
The top 10 Authors currently are Costa, Thomas, Beckett, Storb, Snyder, Lefkowitz, Mandel, Weiden, Meister, and Janssen. Costa, Thomas, Beckett, and Storb all have over **30** publications, while Snyder, Lefkowitz, Mandel, Weiden, Meister, and Janssen have over **21** publications. 

## Summary table of top journal with the most articles per year
```{r, echo=FALSE, message=FALSE}
mysql_query <- "SELECT journal_title, SUM(num_a_year) 
FROM JournalFact 
GROUP BY journal_title 
ORDER BY SUM(num_a_year) DESC 
LIMIT 1"

top_journal = suppressWarnings(dbGetQuery(dbcon_mysqlJ, mysql_query))

kable(top_journal, align = c("l", "l"), col.names = c("Journal Title", "Average Articles per Year"))
```
The top journal is the **Biochimica et biophysica acta** with **920** articles per year on average. 

```{r, echo=FALSE, message=FALSE}
invisible({dbDisconnect(dbcon_mysqlJ)})
invisible({dbDisconnect(dbcon_mysqlA)})
```

